### 2020-10-22 thesis/chap_2.tex
define accronyms, comment 33

Scenarios have been widely applied in conservation research, both at global \citep{tscharntke_global_2012, brussaard_reconciling_2010}, regional and local \citep{carlson_scenario_2011, delevaux_scenario_2018} scales. In a participatory setting, other methods can be used to help in scenario design: those methods include participatory mapping, a participatory GIS method. Participatory mapping involves leveraging the knowledge that stakeholders hold about the geography of their landscape, in order to achieve a community-driven objective. It has been widely used in social-ecological research \citep{plieninger_assessing_2013, lynam_review_2007}.

>>>>

Scenarios have been widely applied in conservation research, both at global \citep{tscharntke_global_2012, brussaard_reconciling_2010}, regional and local \citep{carlson_scenario_2011, delevaux_scenario_2018} scales. In a participatory setting, other methods can be used to help in scenario design: those methods include participatory mapping, a participatory GIS method (Geographic Information System). Participatory mapping involves leveraging the knowledge that stakeholders hold about the geography of their landscape, in order to achieve a community-driven objective. It has been widely used in social-ecological research \citep{plieninger_assessing_2013, lynam_review_2007}.

### 2020-10-22 thesis/thesis.tex
define accronyms, comment 33

Connectivity conservation planning (CCP), refers to the enterprise that engages multiple actors such as academics, NGOs, governmental bodies at different scales and in a common goal to conserve and restore the ecological connectivity of the landscape. CCP methods usually involve modelling the connectivity of the landscape of interest and using a prioritization method to determine conservation priorities, and modify land use practices to conserve or improve connectivity. This thesis  contributes to an ongoing CCP in Montérégie, in southern Québec. In the following, we introduce connectivity modelling. We then introduce the study region and describe previous CCP and research. We point out ways in which CCP methods can be improved and how this thesis contributes to doing so. We then introduce the two other key concepts of the thesis: land use change modelling and participatory methods. \\ \vspace{2em}

@@

This thesis has two chapters.  In the first chapter, we combined a connectivity model, using circuit theory, with a land use and climate change model that uses a combination of statistical modelling and MCMC-based simulations. In the second chapter, we ran a stakeholder workshop to derive conservation priorities and use those results as inputs to derive simple, community driven, alternative conservation scenarios. We also compare and contrast the results of these scenarios and discuss the importance of considering stakeholder inputs to produce a resilient network of protected areas. \\
}%
\Intro

>>>>

Connectivity conservation planning (CCP), refers to the enterprise that engages multiple actors such as academics, NGOs (Non-Governmental Organizations), governmental bodies at different scales and in a common goal to conserve and restore the ecological connectivity of the landscape. CCP methods usually involve modelling the connectivity of the landscape of interest and using a prioritization method to determine conservation priorities, and modify land use practices to conserve or improve connectivity. This thesis  contributes to an ongoing CCP in Montérégie, in southern Québec. In the following, we introduce connectivity modelling. We then introduce the study region and describe previous CCP and research. We point out ways in which CCP methods can be improved and how this thesis contributes to doing so. We then introduce the two other key concepts of the thesis: land use change modelling and participatory methods. \\ \vspace{2em}

@@

This thesis has two chapters.  In the first chapter, we combined a connectivity model, using circuit theory, with a land use and climate change model that uses a combination of statistical modelling and MCMC-based simulations (Markov Chain Monte Carlo). In the second chapter, we ran a stakeholder workshop to derive conservation priorities and use those results as inputs to derive simple, community driven, alternative conservation scenarios. We also compare and contrast the results of these scenarios and discuss the importance of considering stakeholder inputs to produce a resilient network of protected areas. \\
}%
\Intro
